UCD\\MSc Thesis Proposal:\\\emph{An Approach To Continuous Capacity Planning In Cloud Environment With Uptime Based Pricing Model}

### 2014-06-20 paper/proposal.tex
project tasks added

\title{UCD\\MSc Thesis Proposal:\\\emph{A Near Real Time System For Continuous Capacity Planning in Cloud Environment With Dynamic Pricing Based On Uptime}}
\author{Kamil Smuga}
\date{\today}

@@

New IaaS solutions are becoming available with a growing number of supported pricing models. This makes the offering attractive enough to move the entire businesses to the Cloud. The availability of different pricing schemes based on resource utilisation and uptime reveals new challenges in already unpredictive Capacity Planning process. Is it better to pay some amount of money upfront and less hourly rate? Is is better to invest in less heavy utilized instances or maybe in more medium ones? When exactly one pricing scheme becomes more attractive?

@@

>>>>

\title{UCD\\MSc Thesis Proposal:\\\emph{An Approach To Continuous Capacity Planning In Cloud Environment With Uptime Based Pricing Model}}
\author{Kamil Smuga}
\date{\today}

@@

New IaaS solutions are becoming available with a growing number of supported pricing models. This makes the offering attractive enough to move the entire businesses to the Cloud. The availability of different pricing schemes based on resource utilisation and uptime reveals new challenges in already unpredictive capacity planning process. Is it better to pay some amount of money upfront and less hourly rate? Is is better to invest in less heavy utilized instances or maybe in more medium ones? When exactly one pricing scheme becomes more cost effective?

@@

  \section{Project tasks}

  \begin{itemize}
  \item Mandatory:
    \begin{itemize}
      \item A formal definition of continous capacity planning approach.
      \item A design of an algorithm that calculates an uptime optimality factor of VM utilisation based on a pricing scheme.
    \end{itemize}

  \item Discretionary
    \begin{itemize}
      \item An integration with an IaaS provider's API to feed data into the system.
      \item A graphical representation of results calculated by the algorithm.
    \end{itemize}

  \item Exceptional
    \begin{itemize}
      \item Generate suggestions to change the configuration based on the calculated results.
    \end{itemize}
